---
title: "Spatial pattern of plant species' biodiversity in South Africa"
author: "Qianru Liao"
date: "2018年11月12日"
output: html_document
---
### Introduction
Fuguring out the pattern of distribution of species richness and the pattern spatial turnover of plant species are necessary for identifying target areas in species conservation. And this pattern can not be divorced from spatial scale. Comparing the pattern in different spatial scale will give a conprehensive imformation for helping conserving plant species.

# **Problem / Question**
1.What is the pattern of bird species richness in South Africa?
2.what is the spatial pattern of alpha diversity of plant species in South Africa?
2.What is the spatial pattern of beta diversity of plant species in South Africa?

# **Materials and Methods**
## **Method**
*This study will use the following packages to answer the questions above.
tidyverse
rgdal
sf
foreach
doParallel
registerDoParallel(2)

##**Import Data Sets**
```{r}
library(tidyverse)
library(rgdal)
library(sf)
library(foreach)
library(doParallel)
registerDoParallel(2)
library(fasterize)
library(sp)
library(raster)
library(vegan)
```

###**import shapefiles from each of files**

```{r}
datadir="C:/Users/air/Desktop/projectR/"
files=data.frame(
  path=list.files(datadir, recursive=T, pattern="shp$"),stringsAsFactors = F)%>%
  mutate(file=basename(path),
         species=gsub(".shp","",file),
         family=gsub("[/].*$","",path))
all_species = foreach(i=1:nrow(files),.combine=rbind,.packages = c("dplyr","sf")) %dopar% {
  sp=read_sf(file.path(datadir,files$path[i]))%>%
    select(-1)%>%
    mutate(family=files$family[i],species=files$species[i]) %>% st_set_crs(4326)
  #return(st_crs(sp))
    return(sp)
}
```

###**Spatial Richness Map**
```{r}
cfr_bbox=st_bbox(all_species)
r <- raster(
            xmn=cfr_bbox$xmin, 
            xmx=cfr_bbox$xmax, 
            ymn=cfr_bbox$ymin, 
            ymx=cfr_bbox$ymax,
            res=0.1)

raster_spatial_richness<- fasterize(all_species, r, background = 0, fun = "sum", by = NULL)
plot(raster_spatial_richness)
```

###**Spatial pattern of alpha biodiversity**
```{r}
raster_alphadiversity<- fasterize(all_species, r, background = 0, by = "species")
raster_alphadiversity1<- fasterize(all_species, r, background = 0, by = NULL)
all_alphadiversity=as.data.frame(raster_alphadiversity)
library(vegan)
simpson<- all_alphadiversity %>%diversity(index="simpson")
`values<-`(raster_alphadiversity1, simpson)
plot(raster_alphadiversity1)
```

#**Conclusion**
What have you learned? Are there any broader implications?

#**References**
